Spatial Analysis of Russian Law Firms Naming

### 2024-07-18 law-firms-names/Paper.Rmd
Write a paragraph about FTS data processing abd a paragraph about text embeddings, #5

>>>>

### 2.2.1. FTS data processing

SMB registry dumps from FTS website have a large volume (≈200 Gb in total) and a complex structure: each dump is an archive of several thousand XML files, and each XML file contain 900 records with various information about organisations and individuals. Dumps are monthly, resulting in ≈90 archives for the period from 2016 to the present. If unpacked, all archives would occupy more than 2 Tb of disk space, and the extraction and preprocessing of such volume of data would take a large time. It should be noted, though, that the majority of information is redundant for the task in hand, because it is duplicated due to data publication specific (each archive contains a full copy of the registry, and if nothing has changed during the month, the data records will be merely the same) and because only the data about law firms is required, while the registry holds information about all the other firms as well. To extract necessary data from the raw archives, an open-source Python command-line tool was developed named ru-smb-companies. The main stages of data extractions are outlined in the next paragraph, while for the complete information about data processing workflow readers may refer to the source code of the program.

FTS data processing took several steps. First, all source archives available at the time of research (November 2023) were downloaded  from FTS servers and stored both locally and in the cloud. Next, information about law firms was extracted from each archive to a CSV file. Extracted attributes include company or person name, address of incorporation (region, district, city, settlement), taxpayer ID, main activity code and some other properties. After this, CSV tables were combined into one table, deduplicated, and raw addresses were normalized and geocoded to fix the inconsistency in location names and add geographical coordinates. Finally, the resulting table was transformed in a panel view so that each row represents one business entity at a given year. The output table contains data about ≈ 30, 000 law firms for 2016–23.

### 2.2.2. Firm names processing

A major challenge regarding the methods of this study is the working with names. The objectives of the research imply that names should be grouped and compared in some way. This can easily be accomplished with numbers, but firm names are just short text sequences. Of course, a human can easily say whether two names are similar or not and classify them. However, the human-based approach does not scale well, and the quantity of names requires automation. There are several traditional techniques allowing us to compare text strings. For example, edit distance calculates the number of atomic changed required to turn one string to another, and the edit distance between “cat” and “car” is 1, while the edit distance between “car” and “karst” is 3. Another method named n-gram similarity splits the strings into subsequences, or tokens, and finds the number of common tokens, so that “law company” and “law bureau” are more close to each other than “law bureau” and “juridical center”. Despite their simplicity, they also have a significant disadvantage: they cannot account for the intrinsic variability and flexibility of language and do not consider the meaning of the words and phrases rather than their formal representation. For instance, a human understands that “law company” and “legal organisation” mean almost the same, while edit distance between these strings is high, and n-gram similarity is low. A modern method called text embeddings (sometimes referred to as vectors) can deal with this issue and therefore it is used for this research.
